Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Added cross-references for the appendices.

A detailed account about the methodology of a pollster found within the data obtained from 538 along with an idealized methodology and survey can be found in the Appendix (SECTION).

@@

# Appendix {#sec-appendix}

## Pollster Methodology

@@

## Idealized Pollster Methodology

@@

# Copy of the survey questions

>>>>

A detailed account about the methodology of a pollster found within the data obtained from 538 along with an idealized methodology and survey can be found in the Appendix (@sec-pollster, @sec-survey).

@@

# Appendix

## Pollster Methodology {#sec-pollster}

@@

## Idealized Pollster Methodology {#sec-survey}

@@

## Copy of the survey questions
